---
title: "Test-1-af-quarto"
author: "MZS"
format: html
---

## Keep it simple, stupid (R)

```{r}
1 + 1
```

## Setup Chunkus

```{r setup}
#| message: false
library(tidyverse)
post_meal_data <- read_csv2(
  here::here("data/post-meal-insulin.csv")
)

small_post_meal_data <- select(post_meal_data, id, Age, BMI, Group, auc_pg, auc_ins, glykemi)

tidier_post_meal_data <- small_post_meal_data |>
  rename(
    auc_glucose = auc_pg,
    auc_insulin = auc_ins
  ) |>
  filter(glykemi == 0) |>
  select(-glykemi)

tidied_post_meal_data <- tidier_post_meal_data |>
  mutate(
    insulin_glucose_ratio = auc_insulin / auc_glucose,
    Group = if_else(Group == "CTR", "Control", "First-degree relative")
  )
```

## About Me

- Dude: Michael
- Place: SDCC
- Stuff: Diabetes Research

I *like* **trains**

## Simple Code or not?

```{r}
3 * 3
```

## Testing for GIT
Should you git gut or gut git? You got to git it. Gut.

## Showing gut GIT data

```{r}
post_meal_data
```

```{r}
glimpse(post_meal_data)
```


```{r}
#| fig-cap: "Distribution of BMI"
#| label: fig-bmi-histo
#| message: false
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

@fig-bmi-histo

## New gut bar plot for Git

```{r}
#| message: false
#| fig-cap: "Group allocation count"
#| label: fig-group-bar
ggplot(post_meal_data, aes(x = Group)) +
  geom_bar()
```

See @fig-group-bar for allocation bar graph

## Fill?

```{r}
post_meal_data |>
  ggplot(aes(x = Group, fill = glykemi)) +
  geom_bar()
```

```{r}
post_meal_data |>
  ggplot(aes(x = Group, fill = as.character(glykemi))) +
  geom_bar()
```

```{r}
post_meal_data |>
  ggplot(aes(x = Group, fill = as.character(glykemi))) +
  geom_bar(position = position_dodge())
```


## Plots side by side

```{r}
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

```{r}
post_meal_data |>
  ggplot(aes(x = Group, fill = as.character(glykemi))) +
  geom_bar(position = position_dodge())
```

```{r side-by-side-figs}
#| label: fig-bmi-group
#| fig-cap: "BMI and Group, side by side"
#| fig-subcap:
#|   - "Distribution of BMI."
#|   - "Group allocation."
#| layout-ncol: 2
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()

post_meal_data |>
  ggplot(aes(x = Group, fill = as.character(glykemi))) +
  geom_bar(position = position_dodge())
```

## Two contiuous variables

```{r}
#| fig-cap: "Scatterplot test"
#| label: fig-scatter-test
```


```{r}
ggplot(post_meal_data, aes(x = BMI, y = auc_pg)) +
  geom_point() +
  geom_smooth()
```


## GITHUB changes?

Or not?

## Selecting data

```{r}
select(post_meal_data, Age, BMI, Weight)
```


```{r}
select(post_meal_data, -Group)
```

```{r}
select(post_meal_data, starts_with("PG"))
```

```{r}
select(post_meal_data, ends_with("DXA"))
```

```{r}
select(post_meal_data, contains("0"))
```


```{r}
small_post_meal_data
```

## PIPES! PIPES EVERYWHERE!!

```{r}
small_post_meal_data |>
  rename(
    auc_glucose = auc_pg,
    auc_insulin = auc_ins
  )
```

## Piping tasks

```{r}
select(post_meal_data, contains("OGTT"))
```

```{r}
post_meal_data |>
  select(
    contains(".."),
    -contains("...")
  ) |>
  rename(
    P.Glucose.minus5.OGTT = P.Glucose..5.OGTT,
    Insulin.minus5.OGTT.X = Insulin..5.OGTT.X
  )
```

```{r}
```


```{r}
post_meal_data |>
  select(id, BMI, Length, Weight, Age) |>
  rename(Height = Length)
```

## Git filters

```{r}
small_post_meal_data |>
  filter(Group == "CTR")
```

```{r}
small_post_meal_data |>
  filter(Group == "CTR", BMI >= 25)

small_post_meal_data |>
  filter(Group == "CTR" | BMI >= 25)
```

## Modify stuff

```{r}
tidier_post_meal_data |>
  mutate(
    insulin_glucose_ratio =
      auc_insulin / auc_glucose,
    Group = if_else(Group == "CTR", "Control", "First-degree relative")
  )
```

## 11.9 exercise

```{r}
post_meal_data |>
  filter(BMI >= 20, BMI <= 40, Group == "FDR")
```

```{r}
post_meal_data |>
  mutate(
    percent_body_fat = (Fat.mass.DXA / Weight) * 100) |>
  filter(percent_body_fat >= 30) |>
select(id, BMI, Length, Weight, Age, percent_body_fat)
```

## Visualize git with jit

```{r}
tidied_post_meal_data |>
  mutate(overweight = if_else(BMI >= 25, "Overweight", "Not overweight")) |>
  ggplot(aes(x = overweight, y = insulin_glucose_ratio)) +
  geom_jitter()
```

### 3 little variable gits

```{r}
tidied_post_meal_data |>
  filter(BMI <= 30) |>
  ggplot(aes(x = Age, y = auc_insulin, colour = Group)) +
  geom_point()
```

```{r}
tidied_post_meal_data |>
  filter(BMI < 30) |>
  mutate(young = if_else(Age < 40, "Young", "Old")) |>
  ggplot(aes(x = BMI, y = insulin_glucose_ratio, colour = Group)) +
  geom_point() +
  facet_grid(rows = vars(young)) +
  labs(
    x = "Body mass index (BMI)",
    y = "Insulin to glucose ratio")
```

## Mad multidimensional gits

```{r}
#| label: fig-multidimensional
#| fig-cap: "Two, mult-dimensional plots of our data."
#| fig-subcap:
#|   - "Distribution of percent body fat by group and age category."
#|   - "Relationship between BMI and bone mineral density, split by insulin sensitivity."
#| layout-ncol: 2
# Task 1.
post_meal_data |>
  mutate(
    percent_body_fat = (Fat.mass.DXA / Weight) * 100,
    young = if_else(Age < 40, "Young", "Old")) |>
  ggplot(aes(x = Group, y = percent_body_fat, colour = young)) +
  geom_jitter(width = 0.2)

# Task 2.
post_meal_data |>
  mutate(
    insulin_glucose_ratio = (auc_ins / auc_pg),
    insulin_insensitive = if_else(insulin_glucose_ratio > mean(insulin_glucose_ratio), "Insensitive", "Sensitive")) |>
  ggplot(aes(x = BMI, y = Bone.mineral.DXA, colour = insulin_insensitive)) +
  geom_point() +
  geom_smooth() +
  facet_grid(cols = vars(insulin_insensitive))
```

## Helping the blind

```{r}
# Tasks 1. and 2.
#| label: fig-bmi-glycemia
#| fig-cap: "BMI and glycemia, side by side."
#| fig-subcap:
#|   - "Distribution of BMI."
#|   - "Number of those with glycemia."
#| layout-ncol: 3
post_meal_data |>
  mutate(hyperglycemia = if_else(glykemi == 1, "Yes", "No")) |>
  ggplot(aes(x = Group, fill = hyperglycemia)) +
  geom_bar(position = position_dodge()) + 
  scale_fill_viridis_d()

post_meal_data |>
  mutate(hyperglycemia = if_else(glykemi == 1, "Yes", "No")) |>
  ggplot(aes(x = Group, fill = hyperglycemia)) +
  geom_bar(position = position_dodge()) + 
  scale_fill_viridis_d(option = "magma")

post_meal_data |>
  mutate(hyperglycemia = if_else(glykemi == 1, "Yes", "No")) |>
  ggplot(aes(x = Group, fill = hyperglycemia)) +
  geom_bar(position = position_dodge()) + 
  scale_fill_viridis_d(option = "cividis")
```


